Significance testing with forward stepwise and grouped forward stepwise model selection

### 2013-09-25 paper/paper.tex
Added first small simulation figure

\usepackage{graphics,amssymb,color}

@@

>>>>

\usepackage{graphics,amssymb,color}
\usepackage{graphicx,subfigure}

@@

\begin{figure}
\begin{center}
\subfigure[Our test]{
\label{fig:lassopvala}
\includegraphics[width=0.5\textwidth]{../figs/small_sim_plot.pdf}}
\hspace{-15pt}
\subfigure[Covariance test]{
\label{fig:lassopvalb}
\includegraphics[width=0.5\textwidth]{../figs/small_sim_plot.pdf}}
\caption{\small \it The left panel shows the empirical distribution
  function of a sample of 20,000 p-values coming
  from a variety of different lasso setups.  The agreement with
  uniform here is excellent.  The right panel shows the empirical
  distribution function of a sample of 10,000 covariance test
  p-values, computed using an $\mathrm{Exp}(1)$ approximation,
  using three different lasso setups.  The
  $\mathrm{Exp}(1)$ approximation is generally conservative.}
\end{center}
\end{figure}
